### 2022-09-28 chapters/benchmarking/conclusion.tex
Proofreading

%  CONCLUSION au lieu de extension

%% maybe add extension as a part of the conclusion for this chapter 
\clearpage
\section{Summary}
there As seen in Section~\cref{sec:soa_benchmarking} of the state of the art, a successful benchmark faces three challenges: reproducibility, accuracy and representativeness. 
This chapter has covered two of the three criteria.

>>>>

\section{Conclusion}
there As seen in Section~\cref{sec:soa_benchmarking} of the state of the art, a successful benchmark faces three challenges: reproducibility, accuracy and representativeness. 
This chapter has covered two of the three criteria.
